Avoiding tipping points in ecosystem based fisheries management: a non-parametric Bayesian approach

### 2014-05-13 manuscripts/manuscript.Rmd
avoid sanitizing math in tables

```{r allen_priors_xtable, include=TRUE, echo=FALSE}
allen_priors_xtable <- data.frame(parameter = c("r0", "K", "theta", "sigma"),
           "lower bound" = c(r0_prior_p[1], K_prior_p[1], theta_prior_p[1], stdQ_prior_p[1]),
           "upper bound" = c(r0_prior_p[2], K_prior_p[2], theta_prior_p[2], stdQ_prior_p[2]))
```

@@

```{r ricker_priors_xtable, include=TRUE, echo=FALSE, cache=FALSE}
ricker_priors_xtable <- data.frame(
  parameter = c("r0", "K", "sigma"),
  "lower bound" = c(r0_prior_p[1], K_prior_p[1], stdQ_prior_p[1]),
  "upper bound" = c(r0_prior_p[2], K_prior_p[2], stdQ_prior_p[2]))
```

@@

```{r myers_prior_xtable, include=TRUE, echo=FALSE} 
myers_priors_xtable <- data.frame(parameter = c("r0", "K", "theta", "sigma"),
           "lower bound" = c(r0_prior_p[1], K_prior_p[1], theta_prior_p[1], stdQ_prior_p[1]),
           "upper bound" = c(r0_prior_p[2], K_prior_p[2], theta_prior_p[2], stdQ_prior_p[2]))
```

@@

```
```{r assemble-opt, dependson=c("gp-opt", "mle-opt", "allen-opt", "ricker-opt", "myers-opt")}
OPT = data.frame(GP = opt_gp$D, True = opt_true$D, MLE = opt_estimated$D, Ricker = opt_ricker$D, Allen = opt_allen$D, Myers = myers_alt$D)
colorkey=cbPalette
names(colorkey) = names(OPT) 
```
```{r sims, dependson="assemble-opt"}
sims <- lapply(OPT, function(D){
  set.seed(1)
  lapply(1:100, function(i) 
    ForwardSimulate(f, p, x_grid, h_grid, x0, D, z_g, profit=profit, OptTime=OptTime)
  )
})

dat <- melt(sims, id=names(sims[[1]][[1]]))
sims_data <- data.table(dat)
setnames(sims_data, c("L1", "L2"), c("method", "reps")) 
# Legend in original ordering please, not alphabetical: 
sims_data$method = factor(sims_data$method, ordered=TRUE, levels=names(OPT))
```

@@

```{r echo=FALSE, results = "asis", include = TRUE, cache=FALSE}
xtable::xtable(ricker_priors_xtable,
  caption = "Parameterization range for the uniform priors in the Ricker model")
```

@@

```{r echo=FALSE, results="asis", include = TRUE, cache=FALSE}
xtable::xtable(myers_priors_xtable,
           caption = "Parameterization range for the uniform priors in the Myers model")
```

@@

```{r echo=FALSE, results = "asis", include=TRUE, cache=FALSE}
xtable::xtable(allen_priors_xtable,
  caption = "Parameterization range for the uniform priors in the Allen model")
```

@@

For simplicity we assume profit function $\Pi_t(X_t, h_t) is linear in the realized harvest, only
enforcing the restriction that harvest can not exceed available stock, that is $\Pi(h,x) = min(h,x)$. $Z_t$ is as previously defined.

>>>>

```{r allen_priors_xtable, include=TRUE, echo=FALSE}
allen_priors_xtable <- data.frame(parameter = c("$r$", "$K$", "$X_C$", "$\\sigma$"),
           "lower bound" = c(r0_prior_p[1], K_prior_p[1], theta_prior_p[1], stdQ_prior_p[1]),
           "upper bound" = c(r0_prior_p[2], K_prior_p[2], theta_prior_p[2], stdQ_prior_p[2]))
```

@@

```{r ricker_priors_xtable, include=TRUE, echo=FALSE, cache=FALSE}
ricker_priors_xtable <- data.frame(
  parameter = c("$r$", "$K$", "$\\sigma$"),
  "lower bound" = c(r0_prior_p[1], K_prior_p[1], stdQ_prior_p[1]),
  "upper bound" = c(r0_prior_p[2], K_prior_p[2], stdQ_prior_p[2]))
```

@@

```{r myers_prior_xtable, include=TRUE, echo=FALSE} 
myers_priors_xtable <- data.frame(parameter = c("$r$", "$K$", "$\\theta$", "$\\sigma$"),
           "lower bound" = c(r0_prior_p[1], K_prior_p[1], theta_prior_p[1], stdQ_prior_p[1]),
           "upper bound" = c(r0_prior_p[2], K_prior_p[2], theta_prior_p[2], stdQ_prior_p[2]))
```

@@

```
```{r assemble-opt, dependson=c("gp-opt", "mle-opt", "allen-opt", "ricker-opt", "myers-opt")}
OPT = data.frame(GP = opt_gp$D, True = opt_true$D, MLE = opt_estimated$D, Ricker = opt_ricker$D, Allen = opt_allen$D, Myers = myers_alt$D)
colorkey=cbPalette
names(colorkey) = names(OPT) 
```
```{r sims, dependson="assemble-opt"}
sims <- lapply(OPT, function(D){
  set.seed(1)
  lapply(1:100, function(i) 
    ForwardSimulate(f, p, x_grid, h_grid, x0, D, z_g, profit=profit, OptTime=OptTime)
  )
})
# turn the list into a data.frame
keep.as.columns <- names(sims[[1]][[1]])
dat <- melt(sims, id=keep.as.columns)
sims_data <- data.table(dat)
setnames(sims_data, c("L1", "L2"), c("method", "reps")) 
# Legend in original ordering please, not alphabetical: 
sims_data$method = factor(sims_data$method, ordered=TRUE, levels=names(OPT))
```

@@

```{r echo=FALSE, results = "asis", include = TRUE, cache=FALSE}
xtable::xtable(ricker_priors_xtable,
  caption = "Parameterization range for the uniform priors in the Ricker model", 
  sanitize.text.function = identity)
```

@@

```{r echo=FALSE, results="asis", include = TRUE, cache=FALSE}
xtable::xtable(myers_priors_xtable,
           caption = "Parameterization range for the uniform priors in the Myers model",
           sanitize.text.function = identity)
```

@@

```{r echo=FALSE, results = "asis", include=TRUE, cache=FALSE}
xtable::xtable(allen_priors_xtable,
  caption = "Parameterization range for the uniform priors in the Allen model",
  sanitize.text.function = identity)
```

@@

For simplicity we assume profit function $\Pi_t(X_t, h_t)$ is linear in the realized harvest, only
enforcing the restriction that harvest can not exceed available stock, that is $\Pi(h,x) = min(h,x)$. $Z_t$ is as previously defined.
